### 2022-12-02 definitions.tex
details

\problemx{$k$-resilience problem for WSTS}
{A state $s$ of a WSTS $(S,\rightarrow, \leq)$, an upward-closed set $I$ with a given basis, a decidable downward-closed set $J$.}
{$\forall s' \in J ~ (s \rightarrow^* s') \implies \exists s'' \in I ~ s' \rightarrow^{\leq k} s''$ ?\newline}

@@

\problemx{bounded Resilience problem for WSTS}
{A state $s$ of a WSTS $(S,\rightarrow, \leq)$, an upward-closed set $U$ with a given basis, a decidable downward-closed set $D$.}
{$\exists k \geq 0 ~ \forall s' \in D ~ (s \rightarrow^* s') \implies \exists s'' \in U ~ s' \rightarrow^{\leq k} s''$ ?\newline}

@@

\begin{proof}
pas de strong.
\end{proof}

>>>>

\problemx{$k$-resilience problem for WSTS}
{A state $s$ of a WSTS $(S,\rightarrow, \leq)$, an upward-closed set $I$ with a given basis, a decidable downward-closed set $J$.}
{$\forall s' ~ (s \rightarrow^* s') \wedge s' \in J  \implies \exists s'' \in I ~ s' \rightarrow^{\leq k} s''$ ?\newline}

@@

\problemx{bounded Resilience problem for WSTS}
{A state $s$ of a WSTS $(S,\rightarrow, \leq)$, an upward-closed set $U$ with a given basis, a decidable downward-closed set $D$.}
{$\exists k \geq 0 ~ \forall s' \in D ~ s \rightarrow^* s' \implies \exists s'' \in U ~ s' \rightarrow^{\leq k} s''$ ?\newline}

@@

\begin{proof}
pas de effective basis of $post^*$.
\end{proof}
